---
title: "p8105_hw1_yw3773"
output: github_document
---
```{r, message=FALSE}
library(tidyverse)
```


## Problem 1

```{r}
# creating the data set
p1_df = tibble(
  num_vec = rnorm(10),
  logical_vec = num_vec > 0,
  char_vec = c('This', 'is', 'my', 'homework', 'one', 'in', 
               'data', 'science','and', 'yeah'),
  fac_vec = factor(c('high', 'median', 'low', 'high', 'high',
                     'low', 'low', 'median', 'median', 'high'))
)

# computing the mean
mean(pull(p1_df, num_vec))
mean(pull(p1_df, logical_vec))
mean(pull(p1_df, char_vec))
mean(pull(p1_df,fac_vec))
```
After I create the data set, when I try to compute the mean, I can only get the mean of the numeric vector and the logical vector. The mean for the character vector and the factor vector shows NA with an error that argument is not numeric or logical: returning NA.

When I try to convert the logical, character, and factor variables to numeric variable, the logical and factor variables can be successfully converted, but the character variable still shows NA. So the character variable cannot be converted to numeric variable and we can not take the mean of it. We can take the mean of logical variable, we can also take the mean of the factor variable if we converted it into numeric.

```{r, eval = FALSE}
as.numeric(pull(p1_df, logical_vec))
as.numeric(pull(p1_df, char_vec))
as.numeric(pull(p1_df, fac_vec))
mean(as.numeric(pull(p1_df, fac_vec)))
```

## Problem 2
```{r}
# load the data
data("penguins", package = "palmerpenguins")
```

The penguins data set has `r ncol(penguins)` columns and `r nrow(penguins)` rows. The variables contains 8 variables which are `r names(penguins)`. The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm.

```{r, warning = FALSE}
# make the plot
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() + 
  ggtitle("The flipper length vs. the bill length \n with respect to species")

ggsave("scatter_plot.pdf", height = 6, width = 5)
```










